{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-30 brains-protocol.tex
4.2 reorganized

The other features --- Age of acquisition, Number of phonemes, Clustering coefficient and Number of synonyms --- do not seem to exhibit any particularly significant effect on susceptibility.
For each of these features, it is indeed possible to draw a constant line which always remains within the respective confidence intervals.  If these variables have an effect, it is by no means as strong as it is for Word frequency.  This is remarkably clear for Clustering coefficient and Number of synonyms, where susceptibility values remain within quite small intervals (respectively [0.09-0.13] and [0.11-0.15]).  We may notice a somewhat marked effect for the highest values of Age of acquisition and Number of phonemes, where the mean susceptibility is almost twice higher than for the rest (respectively 0.19 vs 0.13, and 0.21 vs 0.12).  Keeping in mind the poor statistical significance of this effect, we could still suggest that the longest and late-learnt words are more susceptible.  To examine further this phenomenon, we plotted the two-dimensional map of joint susceptibility values for these two features (heatmap at the bottom right of Fig.~\ref{fig:feature-susceptibilities}).
\TB{We see that \todo{}}.
\TB{This class of words corresponds to \todo{} [\TB{highly specialized words? domain-specific? a hard limit on too complicated words?}]}
%Age of acquisition and Number of phonemes delineate two categories of words: both features have little to no significant effect on susceptibility for low- to mid-valued words, but very high-valued words behave differently and tend to be more substituted (clearly for high Number of phonemes, and only as a tendency for high Age of acquisition).
%These high-valued words also have low occurrence frequencies, which corresponds to the slope change in the frequency curve between extreme low frequency words and mid- to high-frequency words. \rk{check this with a plot of freq vs. clustering and freq vs. AoA, or simply plot of frequency for the high-valued words for AoA and CC.}

@@

We introduce a null hypothesis $\mathcal{H}_0$ to compare the actual variation of a word's feature to its expected variation, assuming the arrival word $\warrival$ has been chosen randomly from the pool of free association words.
In this case, since $\phi(\warrival)$ becomes a constant value in the above averaging (by definition $\warrival$ does not depend on $\wstart$ anymore),  the baseline variation under $\mathcal{H}_0$ may be rewritten as:
$$\nu_{\phi}^0 (f) = \left<\phi\right>$$

We also considered an alternative null hypothesis, denoted $\mathcal{H}_{00}$, where the arrival word is randomly chosen \emph{among immediate synonyms of the start word}, \hbox{i.e.} an arrival word chosen among semantically plausible though still random words.\footnote{In this case $\warrival_{00}$ does depend on $\wstart$.}
The results were not qualitatively different under this second null hypothesis, so for the sake of clarity we chose to keep the simpler~$\mathcal{H}_0$.

Using this method we obtain the mean variation of feature for each start feature value, comparing the variations to a situation where arrival words are chosen randomly.  This gives us a fine-grained view of how word features evolve upon substitution.

\medskip
Results are gathered on Fig.~\ref{fig:feature-variations}.

\rk{Comment results}

\rk{Might want to globally add $y = x$? Defines areas above/below $y = x$ and areas above/below $H_0$}

\begin{itemize}
    \item Clustering: flat, no dependency. But negative bias, which corresponds to literature on word production.
    \item AoA: global negative bias, also consistent with literature. Question: on one side, effect w.r.t. $H_0$ is weaker for higher AoA, but if you compare to $y = x$, it's not that clear.
    \item Frequency: very strong positive bias, ok. Now extreme high-frequency words have a different pattern (maybe a third category at the opposite of the very low-frequency words?): even if above $H_0$, they're brought quite lower than their original value (complexified?)
    \item Number of phonemes and Number of synonyms: expanding behavior (but check with $y = x$): lower goes to lower, higher goes to higher.
\end{itemize}

>>>>

The other features --- Age of acquisition, Number of phonemes, Clustering coefficient and Number of synonyms --- do not seem to exhibit any particularly significant effect on susceptibility.
For each of these features, it is indeed possible to draw a constant line which always remains within the respective confidence intervals.  If these variables have an effect, it is by no means as strong as it is for Word frequency.  This is remarkably clear for Clustering coefficient and Number of synonyms, where susceptibility values remain within quite small intervals (respectively [0.09-0.13] and [0.11-0.15]).  We may notice a somewhat marked effect for the highest values of Age of acquisition and Number of phonemes, where the mean susceptibility is almost twice higher than for the rest (respectively 0.19 vs 0.13, and 0.21 vs 0.12).  Keeping in mind the poor statistical significance of this effect, we could still suggest that the longest and late-learned words are more susceptible.  To examine further this phenomenon, we plotted the two-dimensional map of joint susceptibility values for these two features (heatmap at the bottom right of Fig.~\ref{fig:feature-susceptibilities}).
\TB{We see that \todo{}}.
\TB{This class of words corresponds to \todo{} [\TB{highly specialized words? domain-specific? a hard limit on too complicated words?}]}
%Age of acquisition and Number of phonemes delineate two categories of words: both features have little to no significant effect on susceptibility for low- to mid-valued words, but very high-valued words behave differently and tend to be more substituted (clearly for high Number of phonemes, and only as a tendency for high Age of acquisition).
%These high-valued words also have low occurrence frequencies, which corresponds to the slope change in the frequency curve between extreme low frequency words and mid- to high-frequency words. \rk{check this with a plot of freq vs. clustering and freq vs. AoA, or simply plot of frequency for the high-valued words for AoA and CC.}

@@

Of prime interest is the comparison of the value of $\nu_{\phi}(f)$ with respect to $f$, as it shows whether there is an attraction (or repulsion) effect towards some values of each feature.  In other words, plotting the $y=x$ line, we can see if substitutions tend to converge towards some typical value of a word feature or not --- as is classically done in the study of dynamic systems.

We also introduce a null hypothesis $\mathcal{H}_0$ to compare the actual variation of a word's feature to its expected variation, assuming the arrival word $\warrival$ has been chosen randomly from the pool of free association words.
In this case, since $\phi(\warrival)$ becomes a constant value in the above averaging (by definition $\warrival$ does not depend on $\wstart$ anymore),  the baseline variation under $\mathcal{H}_0$ may be rewritten as:
$$\nu_{\phi}^0 (f) = \left<\phi\right>$$
We thereby obtain the mean variation of feature for each start feature value, comparing the variations to a situation where arrival words are chosen randomly.\footnote{We additionally considered an alternative null hypothesis, denoted $\mathcal{H}_{00}$, where the arrival word is randomly chosen \emph{among immediate synonyms of the start word}, \hbox{i.e.} an arrival word chosen among semantically plausible though still random words. In this case $\warrival_{00}$ does depend on $\wstart$. The results were not qualitatively different under this second null hypothesis, so for the sake of clarity we chose to keep the simpler~$\mathcal{H}_0$.}

\medskip
On the whole, this method gives us a fine-grained view of how word features evolve upon substitution with respect to (i) the original feature (\hbox{vs.} $y=x$) and (ii) a random arrival (\hbox{vs.} $\mathcal{H}_0$).
Results are gathered on Fig.~\ref{fig:feature-variations}.

We can do a first striking observation: all graphs show the existence of a unique intersection of $\nu_{\phi}$ with $y=x$, while the slope of $\nu_{\phi}$ is smaller than 1.  In other words, there exists a unique attractor for all features.  
Second, the comparison with $\mathcal{H}_0$ shows that we have two classes of attractors, depending on whether (i) there is a triple intersection (of $y=x$, $\mathcal{H}_0$ and $\nu_{\phi}$) or (ii) $\mathcal{H}_0$ remains always above or below $\nu_{\phi}$.

\rk{Comment these results} \todo{}

\tb{\begin{itemize}
    \item Clustering: flat, no dependency. But negative bias, which corresponds to literature on word production.
    \item AoA: global negative bias, also consistent with literature. Question: on one side, effect w.r.t. $H_0$ is weaker for higher AoA, but if you compare to $y = x$, it's not that clear.
    \item Frequency: very strong positive bias, ok. Now extreme high-frequency words have a different pattern (maybe a third category at the opposite of the very low-frequency words?): even if above $H_0$, they're brought quite lower than their original value (complexified?)
    \item Number of phonemes and Number of synonyms: expanding behavior (but check with $y = x$): lower goes to lower, higher goes to higher.
\end{itemize}}
